Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2021-07-22 eg6-letters/long-paper/prc-dvcshelium.tex
Update figures for PRC

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_Coh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	coherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
\label{fig:CohPi0Simul}
\end{figure}

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_InCoh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	incoherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
\label{fig:InCohPi0Simul}
\end{figure}

@@

To further evaluate the systematic uncertainty of the measurements, we performed several specialized studies. We 
evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
We also evaluated the impact of changing the binning in $\phi$ on the extraction of the BSA
at 90°. The beam polarization was measured using M\o{}ller scattering runs, the uncertainty was 
estimated based on the known precision of the dedicated apparatus and the spread 
of the measurements during the complete run period. We studied how different methods of
simulating the exclusive $\pi^0$ production affected the single-photon background and
further estimated how much bias could arise from an undetected BSA in the process. As 
radiative corrections are expected to be small
for this process, we did not apply them, but associated an uncertainty equal to their expected value.
These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
evaluated values. They are added quadratically to obtain the total systematic uncertainty presented in the results.

\begin{table}[tbp]
\begin{center}
	\begin{tabular}{|m{4cm}|m{2cm}<{\centering}|m{2.3cm}<{\centering}|m{3.7cm}<{\centering}|}
\hline
\bf Systematic source & \bf  Coherent channel  & \bf Incoherent channel & \bf Type of systematic 
error\\
\hline
Beam polarization &  3.5$\%$ &  3.5$\%$& Normalization\\
\hline
\hline
DVCS cuts & 8 $\%$ &  6 $\%$ & Bin to bin\\
\hline
Data binning & 5.1$\%$ & 7.1$\%$ & Bin to bin\\
\hline
$\pi^0$ subtraction &  0.6$\%$ &  2.0$\%$ & Bin to bin\\
\hline
Radiative corrections &  0.1$\%$ & 0.1$\%$ & Bin to bin\\
\hline
\hline
\textbf{Total bin to bin} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ & Bin to 
bin\\
\hline
\end{tabular}
\caption{The systematic uncertainties on the measured coherent and incoherent 
BSAs at $\phi = 90^{\circ}$.}
\label{Table:systematic_uncertainties}
\end{center}
\end{table}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=15cm]{t_tprime_ALU_90_p_shortscenrario.pdf}
	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
	function of $Q^2$, $x_{B}$ and $-t$, using the photon based $t$ definition (red)
	and the proton based $t^\prime$ definition (black).}
\label{fig:ttpComp}
\end{figure}

@@

\begin{figure}[tbp]
\center
\includegraphics[width=16cm]{Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles~\cite{Airapetian:2009cga}. The theoretical prediction 
	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta dashed line.}
\label{fig:CohALU90}
\end{figure}

We show the extraction of the BSA at 90° in Fig. \ref{fig:CohALU90} together with the 
past HERMES Collaboration results~\cite{Airapetian:2009cga}. Two models are compared to the 
data, they are both based on the hypothesis that the main nuclear effects are 
included by accounting for the nucleon off-shellness and the kinematics of nucleons in nuclei. The 
one by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} 
appears to undershoot the results systematically. However, the more recent and independent 
calculation by Fucini \textit{et al.}~\cite{Fucini:2018gso}, using similar principles but with a non-diagonal nuclear spectral 
function \cite{Viviani:2001wu} based on the AV18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
well. A factor in the difference is that the recent calculation by Fucini {\it et 
al.}~\cite{Fucini:2018gso} benefited from using the precise kinematics of each of the points presented 
in Appendix \ref{sec:fullresults}. Including this information appears to have a significant 
impact on some points, for instance the $-t$ distribution appears to have a peculiar structure 
that is well reproduced when using this information.

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{Coherent_CFF.pdf}
	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
	$-t$ (right panels). The red full line is the theoretical calculation by 
	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
	the blue long dashed line shows the predictions by Liuti {\it et 
	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
\label{fig:CohCFF}
\end{figure}

@@

The results for the measurement of the BSA in the incoherent DVCS channel are presented in
Fig. \ref{fig:InCohALUphi}. They display patterns rather similar to those observed with the 
free proton, with a clear domination of their sinusoidal component. To compare the data to 
models, we extract the BSA at 90° with a fit of the form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$.

The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
calculation by the same groups as presented in Fig. \ref{fig:CohALU90}. We observe a 
significant improvement on the precision compared to 
the HERMES data, which offers more constraint on the models presented. As in the
coherent case, the calculation appears to have issues reproducing the shape of the data,
with Fucini {\it et al.}~\cite{Fucini:2019xlc} doing better than the others.
However, this time the calculations overshoot the data, sometimes by a significant amount.

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_90_p_vs_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line, and 
	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}

@@

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{|c|c|c|c|}
         \hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
  \hline
  1.14  & 0.136 & 0.096 &  0.304  $\pm$ 0.051  $\pm$ 0.032 \\
  1.42  & 0.172 & 0.099 &  0.364  $\pm$ 0.059  $\pm$ 0.037 \\
  1.90  & 0.224 & 0.107 &  0.295  $\pm$ 0.061  $\pm$ 0.028 \\
  \hline 
  1.16  & 0.132 & 0.095 &  0.320  $\pm$ 0.045  $\pm$ 0.038 \\
  1.44  & 0.17  & 0.099 &  0.278  $\pm$ 0.079  $\pm$ 0.027 \\
  1.84  & 0.225 & 0.107 &  0.320  $\pm$ 0.161  $\pm$ 0.037 \\
  \hline 
  1.36  & 0.160 & 0.080 &  0.376  $\pm$ 0.042  $\pm$ 0.033 \\
  1.51  & 0.179 & 0.094 &  0.245  $\pm$ 0.072  $\pm$ 0.031 \\
  1.61  & 0.193 & 0.127 &  0.318  $\pm$ 0.095  $\pm$ 0.035 \\
  \hline
  \end{tabular}
  \caption{Values of the coherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins. }
  \label{table:Coh_BSA_90}
  \end{center}
\end{table}

@@

\begin{table}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
 \hline 
  1.40  & 0.166 & 0.376 & 0.137  $\pm$ 0.022  $\pm$ 0.014 \\   
  1.89  & 0.232 & 0.415 & 0.153  $\pm$ 0.027  $\pm$ 0.017 \\   
  2.34  & 0.288 & 0.497 & 0.190  $\pm$ 0.030  $\pm$ 0.017 \\   
  3.10  & 0.379 & 0.641 & 0.130  $\pm$ 0.041  $\pm$ 0.016 \\   
 \hline 
  1.45  & 0.163 & 0.374 & 0.117  $\pm$ 0.021  $\pm$ 0.012 \\   
  1.93  & 0.225 & 0.381 & 0.177  $\pm$ 0.024  $\pm$ 0.018 \\   
  2.33  & 0.283 & 0.468 & 0.178  $\pm$ 0.031  $\pm$ 0.015 \\   
  2.98  & 0.389 & 0.688 & 0.160  $\pm$ 0.048  $\pm$ 0.014 \\   
 \hline 
  1.84  & 0.215 & 0.135 & 0.183  $\pm$ 0.021  $\pm$ 0.014 \\   
  2.15  & 0.257 & 0.281 & 0.141  $\pm$ 0.027  $\pm$ 0.020 \\   
  2.37  & 0.291 & 0.492 & 0.137  $\pm$ 0.029  $\pm$ 0.024 \\   
  2.45  & 0.312 & 1.089 & 0.139  $\pm$ 0.062  $\pm$ 0.024 \\   
 \hline
 \end{tabular}
 \caption{Values of the incoherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins.}
 \label{table:InCoh_BSA_90}
 \end{center}
\end{table}

>>>>

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_Coh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	coherent exclusive $\pi^0$ production as a function of $x$ (panel a), 
        $Q^2$ (panel b), $-t$ (panel c) and $\phi$ (panel d).}
\label{fig:CohPi0Simul}
\end{figure}

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_InCoh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	incoherent exclusive $\pi^0$ production as a function of $x$ (panel a), 
        $Q^2$ (panel b), $-t$ (panel c) and $\phi$ (panel d).}
\label{fig:InCohPi0Simul}
\end{figure}

@@

To further evaluate the systematic uncertainty of the measurements, we performed several specialized studies. We 
evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
We also evaluated the impact of changing the binning in $\phi$ on the extraction of the BSA
at 90 degrees. The beam polarization was measured using M\o{}ller scattering runs, the uncertainty was 
estimated based on the known precision of the dedicated apparatus and the spread 
of the measurements during the complete run period. We studied how different methods of
simulating the exclusive $\pi^0$ production affected the single-photon background and
further estimated how much bias could arise from an undetected BSA in the process. As 
radiative corrections are expected to be small
for this process, we did not apply them, but associated an uncertainty equal to their expected value.
These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
evaluated values. They are added quadratically to obtain the total systematic uncertainty presented in the results.

\begin{table}[tbp]
\begin{center}
	\begin{tabular}{|m{4cm}|m{2cm}<{\centering}|m{2.3cm}<{\centering}|m{3.7cm}<{\centering}|}
\hline
\bf Systematic source & \bf  Coherent channel  & \bf Incoherent channel & \bf Type of systematic 
error\\
\hline
Beam polarization &  3.5$\%$ &  3.5$\%$& Normalization\\
\hline
\hline
DVCS cuts & 8 $\%$ &  6 $\%$ & Bin to bin\\
\hline
Data binning & 5.1$\%$ & 7.1$\%$ & Bin to bin\\
\hline
$\pi^0$ subtraction &  0.6$\%$ &  2.0$\%$ & Bin to bin\\
\hline
Radiative corrections &  0.1$\%$ & 0.1$\%$ & Bin to bin\\
\hline
\hline
\textbf{Total bin to bin} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ & Bin to 
bin\\
\hline
\end{tabular}
\caption{The systematic uncertainties on the measured coherent and incoherent 
BSAs at $\phi = 90$~deg.}
\label{Table:systematic_uncertainties}
\end{center}
\end{table}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=15cm]{t_tprime_ALU_90_p_shortscenrario.pdf}
	\caption{The BSA at 90 degrees ($A_{LU}^{Incoh} (90~\mathrm{deg})$) as a
	function of $Q^2$ (panel a), $x_{B}$ (panel b) and $-t$ (panel c), using the photon based $t$ definition (red)
	and the proton based $t^\prime$ definition (black).}
\label{fig:ttpComp}
\end{figure}

@@

\begin{figure}[tbp]
\center
\includegraphics[width=16cm]{Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90 degrees as a function of $Q^2$ (panel a), $x$ (panel b) and $-t$ (panel c).
	Our results are shown with black squares, HERMES results 
	with green circles~\cite{Airapetian:2009cga}. The theoretical prediction 
	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta dashed line.}
\label{fig:CohALU90}
\end{figure}

We show the extraction of the BSA at 90 degrees in Fig. \ref{fig:CohALU90} together with the 
past HERMES Collaboration results~\cite{Airapetian:2009cga}. Two models are compared to the 
data, they are both based on the hypothesis that the main nuclear effects are 
included by accounting for the nucleon off-shellness and the kinematics of nucleons in nuclei. The 
one by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} 
appears to undershoot the results systematically. However, the more recent and independent 
calculation by Fucini \textit{et al.}~\cite{Fucini:2018gso}, using similar principles but with a non-diagonal nuclear spectral 
function \cite{Viviani:2001wu} based on the AV18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
well. A factor in the difference is that the recent calculation by Fucini {\it et 
al.}~\cite{Fucini:2018gso} benefited from using the precise kinematics of each of the points presented 
in Appendix \ref{sec:fullresults}. Including this information appears to have a significant 
impact on some points, for instance the $-t$ distribution appears to have a peculiar structure 
that is well reproduced when using this information.

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{Coherent_CFF.pdf}
	\caption{The imaginary part of the helium-4 CFF $\mathcal{H}_A$ is shown as 
        a function of $Q^2$ (panel a), $x$ (panel b) and 
	$-t$ (panel c). The real part of the helium-4 CFF $\mathcal{H}_A$ is shown as 
        a function of $Q^2$ (panel d), $x$ (panel e) and 
	$-t$ (panel f). The red full line is the theoretical calculation by 
	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
	the blue long dashed line shows the predictions by Liuti {\it et 
	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
\label{fig:CohCFF}
\end{figure}

@@

The results for the measurement of the BSA in the incoherent DVCS channel are presented in
Fig. \ref{fig:InCohALUphi}. They display patterns rather similar to those observed with the 
free proton, with a clear domination of their sinusoidal component. To compare the data to 
models, we extract the BSA at 90 degrees with a fit of the form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$.

The asymmetries at 90 degrees are presented in Fig. \ref{fig:IncALU} together with the theoretical
calculation by the same groups as presented in Fig. \ref{fig:CohALU90}. We observe a 
significant improvement on the precision compared to 
the HERMES data, which offers more constraint on the models presented. As in the
coherent case, the calculation appears to have issues reproducing the shape of the data,
with Fucini {\it et al.}~\cite{Fucini:2019xlc} doing better than the others.
However, this time the calculations overshoot the data, sometimes by a significant amount.

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_90_p_vs_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90 degrees as a function of $Q^2$ (panel a), $-t$ (panel b) 
        and $x_B$ (panel c). Our measurement is represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (panel a), $-t$ (panel b) and $x_B$ (panel c). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line, and 
	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}

@@

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{|c|c|c|c|}
         \hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90 deg) $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
  \hline
  1.14  & 0.136 & 0.096 &  0.304  $\pm$ 0.051  $\pm$ 0.032 \\
  1.42  & 0.172 & 0.099 &  0.364  $\pm$ 0.059  $\pm$ 0.037 \\
  1.90  & 0.224 & 0.107 &  0.295  $\pm$ 0.061  $\pm$ 0.028 \\
  \hline 
  1.16  & 0.132 & 0.095 &  0.320  $\pm$ 0.045  $\pm$ 0.038 \\
  1.44  & 0.17  & 0.099 &  0.278  $\pm$ 0.079  $\pm$ 0.027 \\
  1.84  & 0.225 & 0.107 &  0.320  $\pm$ 0.161  $\pm$ 0.037 \\
  \hline 
  1.36  & 0.160 & 0.080 &  0.376  $\pm$ 0.042  $\pm$ 0.033 \\
  1.51  & 0.179 & 0.094 &  0.245  $\pm$ 0.072  $\pm$ 0.031 \\
  1.61  & 0.193 & 0.127 &  0.318  $\pm$ 0.095  $\pm$ 0.035 \\
  \hline
  \end{tabular}
  \caption{Values of the coherent $A_{LU}$(90 deg) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins. }
  \label{table:Coh_BSA_90}
  \end{center}
\end{table}

@@

\begin{table}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90 deg) $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
 \hline 
  1.40  & 0.166 & 0.376 & 0.137  $\pm$ 0.022  $\pm$ 0.014 \\   
  1.89  & 0.232 & 0.415 & 0.153  $\pm$ 0.027  $\pm$ 0.017 \\   
  2.34  & 0.288 & 0.497 & 0.190  $\pm$ 0.030  $\pm$ 0.017 \\   
  3.10  & 0.379 & 0.641 & 0.130  $\pm$ 0.041  $\pm$ 0.016 \\   
 \hline 
  1.45  & 0.163 & 0.374 & 0.117  $\pm$ 0.021  $\pm$ 0.012 \\   
  1.93  & 0.225 & 0.381 & 0.177  $\pm$ 0.024  $\pm$ 0.018 \\   
  2.33  & 0.283 & 0.468 & 0.178  $\pm$ 0.031  $\pm$ 0.015 \\   
  2.98  & 0.389 & 0.688 & 0.160  $\pm$ 0.048  $\pm$ 0.014 \\   
 \hline 
  1.84  & 0.215 & 0.135 & 0.183  $\pm$ 0.021  $\pm$ 0.014 \\   
  2.15  & 0.257 & 0.281 & 0.141  $\pm$ 0.027  $\pm$ 0.020 \\   
  2.37  & 0.291 & 0.492 & 0.137  $\pm$ 0.029  $\pm$ 0.024 \\   
  2.45  & 0.312 & 1.089 & 0.139  $\pm$ 0.062  $\pm$ 0.024 \\   
 \hline
 \end{tabular}
 \caption{Values of the incoherent $A_{LU}$(90 deg) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins.}
 \label{table:InCoh_BSA_90}
 \end{center}
\end{table}
